---
title: "Final_Project_Part_4_A"
author: "Peng Yuan"
date: '2023-04-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  Interpretation – ivA) Input Importance
### 1. Load package and model
```{r}
library(caret)
library(tidyverse)
library(yardstick)
library(gbm)
```

```{r}
fit_reg_nnet_tune <- readr::read_rds('Model/fit_reg_nnet_tune.rds')
acc_gbm_tune <- readr::read_rds('Model/acc_gbm_tune.rds')
```


### 2. Identify the most important variables
#### 2.1 Regression Model
```{r}
plot(varImp(fit_reg_nnet_tune), top = 10)
```

#### 2.2 Classification Model
```{r}
plot(varImp(acc_gbm_tune),top = 10)
```


#### Are the most important variables similar for the regression and classification tasks?
No, they are not similar with each other.

#### Does one of the color model INPUTS “dominate” the other variables? 
No.R,G and B are not dominate others variables both in regression model and in classification model.

#### Does one of the color model INPUTS appear to be not helpful at all?
No. Although every color input have different importance, but all of them are helpful. 

#### Based on your modeling results, do you feel the color model INPUTS alone help identify POPULAR paints????
No, we can't just use color model inputs. We can see that the Lightness-deep is the most important features in the best regression model and the Saturation-gray is also important in the best classification model. So, we can't use color model imputs along to identify popular paints.  













