---
title: "Final_Project_Part_2_C"
author: "Peng Yuan"
date: '2023-04-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## iiC) Linear models Predictions
### 1. Load package, data and model
#### 1.1 Load package
```{r,1.1_solution}
library(tidyverse)
library(caret)
library(coefplot)
library(rstanarm)
library(splines)
```

#### 1.2 Load data
```{r,1.2_solution}
df <- readr::read_csv("paint_project_train_data.csv", col_names = TRUE)

dfii_ready <- df %>% 
  mutate(y = boot::logit( (response - 0) / (100 - 0) ) ) %>% 
  subset(select = c(R, G, B, 
         Lightness, Saturation, Hue,response,
         y))


dfii <- dfii_ready %>%
  subset(select = c(R, G, B, Hue)) %>% 
  scale() %>% as.data.frame() %>%
  bind_cols(dfii_ready %>% subset(select = c(Lightness, Saturation, y)))



dfii %>% glimpse()
```

### 1.3 Load model
```{r}
mod5 <- lm(y ~ (R + G + B + Hue) * (Saturation + Lightness), dfii)

mod10 <- lm(y ~ (I(R^2) + I(G^2) + I(B^2) + I(Hue^2) + R * G * B * Hue) + (Saturation * Lightness), dfii)
```


```{r}
stan_lm_mod5 <- stan_lm(formula(mod5), 
                         data = dfii, 
                         prior = R2(location = 0.75),
                         chains = 1,
                         iter = 300,
                         seed = 123123,
                         refresh = 0)
```

```{r}
stan_lm_mod10 <- stan_lm(formula(mod10), 
                         data = dfii, 
                         prior = R2(location = 0.75), 
                         seed = 123123,
                         chains = 1,
                         iter = 300,
                         refresh = 0)
```




### 2 Predictions -  Bayesian Model
#### 2.1 Build prediction model

```{r,2.1_build model}
viz_grid <- expand.grid(R = seq(min(dfii$R), max(dfii$R), length.out = 25),
                        G = median(dfii$G),
                        B = median(dfii$B),
                        Lightness = "dark",
                        Saturation = "gray",
                        Hue = quantile(dfii$Hue, 
                                           probs = c(0.05, 0.25, 0.5, 0.75, 0.95), 
                                           na.rm = TRUE),
                        KEEP.OUT.ATTRS = FALSE,
                        stringsAsFactors = FALSE) %>% 
  as.data.frame() %>% tibble::as_tibble()

viz_grid %>% glimpse()
```

#### 2.2 Draw predictive mean trend
**model 5**
```{r}
posterior_predict(stan_lm_mod5, newdata = viz_grid) %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  tibble::rowid_to_column("post_id") %>% 
  pivot_longer(!c("post_id"), names_to = 'pred_id') %>% 
  mutate(across(.cols = 'pred_id', .fns = as.numeric)) %>% 
  group_by(pred_id) %>% 
  summarise(num_post = n(),
            y_avg = mean(value),
            y_lwr = quantile(value, 0.05),
            y_upr = quantile(value, 0.95)) %>% 
  ungroup() %>% 
  left_join(viz_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>% 
  ggplot(mapping = aes(x = R)) +
  geom_ribbon(mapping = aes(ymin = y_lwr,
                            ymax = y_upr,
                            group = Hue,
                            fill = as.factor(Hue)),
              alpha = 0.5) +
  geom_line(mapping = aes(y = y_avg,
                          group = Hue,
                          color = as.factor(Hue)),
            size = 1.) +
  facet_wrap(~Lightness, labeller = "label_both") +
  scale_fill_viridis_d("Hue") +
  scale_color_viridis_d("Hue") +
  labs(y = "y") +
  theme_bw() +
  theme(legend.position = "top")
```

**model 10**
```{r}
posterior_predict(stan_lm_mod10, newdata = viz_grid) %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  tibble::rowid_to_column("post_id") %>% 
  pivot_longer(!c("post_id"), names_to = 'pred_id') %>% 
  mutate(across(.cols = 'pred_id', .fns = as.numeric)) %>% 
  group_by(pred_id) %>% 
  summarise(num_post = n(),
            y_avg = mean(value),
            y_lwr = quantile(value, 0.05),
            y_upr = quantile(value, 0.95)) %>% 
  ungroup() %>% 
  left_join(viz_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>% 
  ggplot(mapping = aes(x = R)) +
  geom_ribbon(mapping = aes(ymin = y_lwr,
                            ymax = y_upr,
                            group = Hue,
                            fill = as.factor(Hue)),
              alpha = 0.5) +
  geom_line(mapping = aes(y = y_avg,
                          group = Hue,
                          color = as.factor(Hue)),
            size = 1.) +
  facet_wrap(~Lightness, labeller = "label_both") +
  scale_fill_viridis_d("Hue") +
  scale_color_viridis_d("Hue") +
  labs(y = "y") +
  theme_bw() +
  theme(legend.position = "top")
```

####  2.3 Confidence interval on the mean and Prediction interval
**Model 5**
```{r}
posterior_predict(stan_lm_mod5, newdata = viz_grid) %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  tibble::rowid_to_column("post_id") %>% 
  pivot_longer(!c("post_id"), names_to = 'pred_id') %>% 
  mutate(across(.cols = 'pred_id', .fns = as.numeric)) %>% 
  group_by(pred_id) %>% 
  summarise(y_avg = mean(value),
            y_lwr = quantile(value, 0.05),
            y_upr = quantile(value, 0.95)) %>% 
  ungroup() %>% 
  left_join(posterior_linpred(stan_lm_mod5, newdata = viz_grid) %>% 
              as.data.frame() %>% tibble::as_tibble() %>% 
              tibble::rowid_to_column("post_id") %>% 
              pivot_longer(!c("post_id"), names_to = 'pred_id') %>% 
              mutate(across(.cols = 'pred_id', .fns = as.numeric)) %>% 
              group_by(pred_id) %>% 
              summarise(trend_avg = mean(value),
                        trend_lwr = quantile(value, 0.05),
                        trend_upr = quantile(value, 0.95)) %>% 
              ungroup(),
            by = "pred_id") %>% 
  left_join(viz_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>% 
  ggplot(mapping = aes(R)) +
  geom_ribbon(mapping = aes(ymin = y_lwr, ymax = y_upr,
                            group = Hue), 
              fill = "darkorange") +
  geom_ribbon(mapping = aes(ymin = trend_lwr, ymax = trend_upr,
                            group = Hue),
              fill = "grey") +
  geom_line(mapping = aes(y = trend_avg,
                          group = Hue),
            color = "black", size = 0.85) +
  facet_wrap(~Hue, labeller = "label_both") +
  labs(y = "y") +
  theme_bw()
```
**Model 10**
```{r}
posterior_predict(stan_lm_mod10, newdata = viz_grid) %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  tibble::rowid_to_column("post_id") %>% 
  pivot_longer(!c("post_id"), names_to = 'pred_id') %>% 
  mutate(across(.cols = 'pred_id', .fns = as.numeric)) %>% 
  group_by(pred_id) %>% 
  summarise(y_avg = mean(value),
            y_lwr = quantile(value, 0.05),
            y_upr = quantile(value, 0.95)) %>% 
  ungroup() %>% 
  left_join(posterior_linpred(stan_lm_mod10, newdata = viz_grid) %>% 
              as.data.frame() %>% tibble::as_tibble() %>% 
              tibble::rowid_to_column("post_id") %>% 
              pivot_longer(!c("post_id"), names_to = 'pred_id') %>% 
              mutate(across(.cols = 'pred_id', .fns = as.numeric)) %>% 
              group_by(pred_id) %>% 
              summarise(trend_avg = mean(value),
                        trend_lwr = quantile(value, 0.05),
                        trend_upr = quantile(value, 0.95)) %>% 
              ungroup(),
            by = "pred_id") %>% 
  left_join(viz_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>% 
  ggplot(mapping = aes(R)) +
  geom_ribbon(mapping = aes(ymin = y_lwr, ymax = y_upr,
                            group = Hue), 
              fill = "darkorange") +
  geom_ribbon(mapping = aes(ymin = trend_lwr, ymax = trend_upr,
                            group = Hue),
              fill = "grey") +
  geom_line(mapping = aes(y = trend_avg,
                          group = Hue),
            color = "black", size = 0.85) +
  facet_wrap(~Hue, labeller = "label_both") +
  labs(y = "y") +
  theme_bw()
```

#### 2.4 
**Model 5**
```{r}
posterior_predict(stan_lm_mod5, newdata = viz_grid) %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  tibble::rowid_to_column("post_id") %>% 
  pivot_longer(!c("post_id"), names_to = 'pred_id') %>% 
  mutate(across(.cols = 'pred_id', .fns = as.numeric)) %>% 
  group_by(pred_id) %>% 
  summarise(num_post = n(),
            y_avg = mean(value),
            y_lwr = quantile(value, 0.05),
            y_upr = quantile(value, 0.95),
            prob_grt_0 = mean(value > 0)) %>% 
  ungroup() %>% 
  left_join(viz_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>% 
  ggplot(mapping = aes(x = R, y = prob_grt_0)) +
  geom_line(mapping = aes(group = Hue,
                          color = as.factor(Hue)),
            size = 1.) +
  scale_fill_viridis_d("Hue") +
  scale_color_viridis_d("Hue") +
  labs(y = "Probability y is greater than 0") +
  theme_bw() +
  theme(legend.position = "top")
```

**Model 10**
```{r}
posterior_predict(stan_lm_mod10, newdata = viz_grid) %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  tibble::rowid_to_column("post_id") %>% 
  pivot_longer(!c("post_id"), names_to = 'pred_id') %>% 
  mutate(across(.cols = 'pred_id', .fns = as.numeric)) %>% 
  group_by(pred_id) %>% 
  summarise(num_post = n(),
            y_avg = mean(value),
            y_lwr = quantile(value, 0.05),
            y_upr = quantile(value, 0.95),
            prob_grt_0 = mean(value > 0)) %>% 
  ungroup() %>% 
  left_join(viz_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>% 
  ggplot(mapping = aes(x = R, y = prob_grt_0)) +
  geom_line(mapping = aes(group = Hue,
                          color = as.factor(Hue)),
            size = 1.) +
  scale_fill_viridis_d("Hue") +
  scale_color_viridis_d("Hue") +
  labs(y = "Probability y is greater than 0") +
  theme_bw() +
  theme(legend.position = "top")
```

**If the predictive trends are consistent between the 2 selected linear models?**
According to the prediction interval and predictive mean trend, I think they are roughly consistence.


