---
title: "Final_Project_Part_1"
author: "Peng Yuan"
date: '2023-04-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Part i: Exploration

### 1. Load package and data
#### 1.1 Load package
```{r,load_package}
library(tidyverse)
```

#### 1.2 Load data
```{r,load_data}
df <- readr::read_csv("paint_project_train_data.csv", col_names = TRUE)

df %>% glimpse()
```

### 2. Visualize the distributions of variables in the data set.

#### 2.1Counts for categorical variables.
```{r,2.1_solution}
df <- df %>% mutate(outcome_event = ifelse(df$outcome == 1, 'event','non_event'))


df %>%
  count(outcome_event) %>%
  ggplot(mapping = aes(x = outcome_event, y = n)) +
  geom_bar(stat = "identity", fill = "steelblue",alpha = 0.8)
```
For categorical variables, the number of events is not balanced with the number of non_events. non_events are significantly more numerous.

#### 2.2 Outcome interact with Saturation
**Histograms or Density plots for continuous variables. Are the distributions Gaussian like?**
```{r}
data.frame(x = df$R) %>% 
  ggplot(aes(x)) +
  geom_density(fill = "steelblue", alpha = 0.5) +
  labs(title = "Density Plot of Variable R", x = "Value of R", y = "Density")

df_bin_R <-df %>% mutate(R_bin = cut(R,
                            breaks = seq(0,300, by = 20),
                            include.lowest = TRUE))

df_bin_R %>% ggplot() +
             geom_bar(mapping = aes(x = R_bin),fill = "steelblue")
```

```{r}
data.frame(x = df$G) %>% 
  ggplot(aes(x)) +
  geom_density(fill = "steelblue", alpha = 0.5) +
  labs(title = "Density Plot of Variable G", x = "Value of G", y = "Density")

df_bin_G <-df %>% mutate(G_bin = cut(G,
                            breaks = seq(0,300, by = 20),
                            include.lowest = TRUE))

df_bin_G %>% ggplot() +
             geom_bar(mapping = aes(x = G_bin),fill = "steelblue")
```

```{r}
data.frame(x = df$B) %>% 
  ggplot(aes(x)) +
  geom_density(fill = "steelblue", alpha = 0.5) +
  labs(title = "Density Plot of Variable B", x = "Value of B", y = "Density")

df_bin_B <-df %>% mutate(B_bin = cut(B,
                            breaks = seq(0,300, by = 20),
                            include.lowest = TRUE))

df_bin_B %>% ggplot() +
             geom_bar(mapping = aes(x = B_bin),fill = "steelblue")
```

```{r}
data.frame(x = df$Hue) %>% 
  ggplot(aes(x)) +
  geom_density(fill = "steelblue", alpha = 0.5) +
  labs(title = "Density Plot of Variable Hue", x = "Value of Hue", y = "Density")

df_bin_Hue <-df %>% mutate(Hue_bin = cut(Hue,
                            breaks = seq(0,40, by = 5),
                            include.lowest = TRUE))

df_bin_Hue %>% ggplot() +
             geom_bar(mapping = aes(x = Hue_bin),fill = "steelblue")
```


R,G and B continuous variables's images look like the distributions Gaussian, but Hue's imagre looks like not.


### Condition (group) the continuous variables based on the categorical variables.

**Are there differences in continuous variable distributions and continuous variable summary statistics based on categorical variable values?**
```{r}
df %>% ggplot(aes(x = R, y = response,color = Lightness)) +
                geom_line(size = 1.2) +
                facet_wrap(~Saturation)

df %>% ggplot(aes(x = G, y = response,color = Lightness)) +
                geom_line(size = 1.2) +
                facet_wrap(~Saturation)

df %>% ggplot(aes(x = B, y = response,color = Lightness)) +
                geom_line(size = 1.2) +
                facet_wrap(~Saturation)


df %>% ggplot(aes(x = Hue, y = response,color = Lightness)) +
                geom_line(size = 1.2) +
                facet_wrap(~Saturation)

df %>% ggplot(aes(x = R + G + B + Hue, y = response,color = Lightness)) +
                geom_line(size = 1.2) +
                facet_wrap(~Saturation)
```

Overall the trend is the same. However, variable B has a slightly different trend in the case of BRIGHT classification and PURE classification.



### Visualize the relationships between the continuous inputs, are they correlated?
```{r}
df_continuous <- df %>%  
  subset(select = -c(outcome,Saturation,Lightness,outcome_event,response))

df_continuous %>%
  cor() %>%
  corrplot::corrplot(type = "upper")
```

Most of the variables are correlated, but the correlation between Hue and response and G is not significant.


### Visualize the relationships between the continuous outputs (response and the LOGIT-transformed response, y) with respect to the continuous INPUTS. 

```{r}
df_logit <- df %>% 
  mutate(y = boot::logit( (response - 0) / (100 - 0) ) ) %>%
  subset(select = c(R, G, B, 
         Lightness, Saturation, Hue,response,
         y))

df_logit %>% glimpse()
```

**Can you identify any clear trends? Do the trends depend on the categorical INPUTS?**
```{r}
df_logit %>% 
  ggplot(mapping = aes(x = R, y = y, color = Lightness))+
  geom_smooth(method = 'loess', formula = y ~ x, size = 0.4)+
  facet_wrap(~Saturation, scales = "free")+
  theme_bw()
```

```{r}
df_logit %>% 
  ggplot(mapping = aes(x = G, y = y, color = Lightness))+
  geom_smooth(method = 'loess', formula = y ~ x, size = 0.4)+
  facet_wrap(~Saturation, scales = "free")+
  theme_bw()
```


```{r}
df_logit %>% 
  ggplot(mapping = aes(x = B, y = y, color = Lightness))+
  geom_smooth(method = 'loess', formula = y ~ x, size = 0.4)+
  facet_wrap(~Saturation, scales = "free")+
  theme_bw()
```

```{r}
df_logit %>% 
  ggplot(mapping = aes(x = Hue, y = y, color = Lightness))+
  geom_smooth(method = 'loess', formula = y ~ x, size = 0.4)+
  facet_wrap(~Saturation, scales = "free")+
  theme_bw()
```


```{r}
df %>% pivot_longer(c(R,G,B,Hue)) %>%
  ggplot(mapping = aes(x = value, y = response)) + 
  geom_point(aes(col = Lightness)) + 
  geom_smooth(aes(fill = Lightness , col = Lightness), formula = y ~ x,method = lm) + 
  facet_wrap(~factor(name,levels = c("R","G","B","Hue")), scales = "free") +
  theme_bw()
```

Yes,I think we can observe a clear upward trend in R,G and B continuous variables, both among the classifications. But in Hue, 








### How can you visualize the behavior of the binary outcome with respect to the continuous inputs? 
```{r}
df %>%
  ggplot(mapping = aes(x = R, y = outcome))+
  geom_point(mapping = aes(color = outcome),size = 0.1)+
  facet_wrap(~Saturation, scales = "free")
```

```{r}
df %>%
  ggplot(mapping = aes(x = G, y = outcome))+
  geom_point(mapping = aes(color = outcome),size = 0.1)+
  facet_wrap(~Saturation, scales = "free")
```

```{r}
df %>%
  ggplot(mapping = aes(x = B, y = outcome))+
  geom_point(mapping = aes(color = outcome),size = 0.1)+
  facet_wrap(~Saturation, scales = "free")
```

```{r}
df %>% 
  ggplot(mapping = aes(x = Saturation)) + 
  geom_bar(aes(fill = as.factor(outcome)),position = 'fill') + 
  scale_fill_brewer(name = 'outcome') + 
  theme_bw()
```

```{r}
df %>% 
  ggplot(mapping = aes(x = Lightness)) + 
  geom_bar(aes(fill = as.factor(outcome)),position = 'fill') + 
  scale_fill_brewer(name = 'outcome') + 
  theme_bw()
```



